Offshore Modeling - Manuscript Model

### 2020-03-06 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
changed statzon 10 to be included with Florida

```{r load data}
seamap <- read_csv(str_c("~/Dropbox/SEAMAP_2019/data/offshore/", 
                        "seamap_manuscriptmods_full.csv"), 
                   col_types = cols()) %>% 
  mutate(year_f = factor(year_f),
         Season = factor(season, levels = c("Summer", "Fall")),
         region = ifelse(region == "Louisiana", "LA West", region),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight", "Florida"))
)

seamap_west <- read_csv(str_c("~/Dropbox/SEAMAP_2019/data/offshore/", 
                        "seamapwest_manuscriptmods_full.csv"), 
                        col_types = cols()) %>% 
  mutate(year_f = factor(year_f),
         Season = factor(season, levels = c("Summer", "Fall")),
         region = ifelse(region == "Louisiana", "LA West", region),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight", "Florida"))
)
```

@@

```{r seamap west stats}
start_year <- min(as.numeric(as.character(seamap_west$survey_year)))
end_year <- max(as.numeric(as.character(seamap_west$survey_year)))
total_catch <- sum(seamap_west$sapidus_catch, na.rm = T)
overall_foa <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3) * 100
overall_mean <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)
percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
station_count <- seamap_west %>% count()

@@

@@

```{r seamap all stats}
start_year <- min(as.numeric(as.character(seamap$survey_year)))
end_year <- max(as.numeric(as.character(seamap$survey_year)))
total_catch <- sum(seamap$sapidus_catch, na.rm = T)
overall_foa <- round(mean(seamap$crab_presence, na.rm = TRUE), 3) * 100
overall_mean <- round(mean(seamap$cpue_towspd, na.rm = T), 3)
percent_zeros <- seamap %>% filter(sapidus_catch == 0) %>% count()
station_count <- seamap %>% count()

>>>>

**NOTE: Statzone 10 donated to Florida**

```{r load data}
seamap <- read_csv(str_c("~/Dropbox/SEAMAP_2019/data/offshore/", 
                        "seamap_manuscriptmods_full.csv"), 
                   col_types = cols()) %>% 
  mutate(year_f = factor(year_f),
         Season = factor(season, levels = c("Summer", "Fall")),
         region = ifelse(statzone == 10, "Florida", region),
         region = ifelse(region == "Louisiana", "LA West", region),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight", "Florida"))
)

seamap_west <- read_csv(str_c("~/Dropbox/SEAMAP_2019/data/offshore/", 
                        "seamapwest_manuscriptmods_full.csv"), 
                        col_types = cols()) %>% 
  mutate(year_f = factor(year_f),
         Season = factor(season, levels = c("Summer", "Fall")),
         region = ifelse(statzone == 10, "Florida", region),
         region = ifelse(region == "Louisiana", "LA West", region),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight", "Florida"))
)
```

@@

```{r seamap west stats}
start_year    <- min(as.numeric(as.character(seamap_west$survey_year)))
end_year      <- max(as.numeric(as.character(seamap_west$survey_year)))
total_catch   <- sum(seamap_west$sapidus_catch, na.rm = T)
overall_foa   <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3) * 100
percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
station_count <- seamap_west %>% count()
overall_mean  <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)
overall_se    <- round(sd(seamap_west$cpue_towspd, na.rm = T) / sqrt(station_count), 3)

@@

 * Overall Standard Error `r overall_se`

@@

```{r seamap all stats}
start_year    <- min(as.numeric(as.character(seamap$survey_year)))
end_year      <- max(as.numeric(as.character(seamap$survey_year)))
total_catch   <- sum(seamap$sapidus_catch, na.rm = T)
overall_foa   <- round(mean(seamap$crab_presence, na.rm = TRUE), 3) * 100
overall_mean  <- round(mean(seamap$cpue_towspd, na.rm = T), 3)
percent_zeros <- seamap %>% filter(sapidus_catch == 0) %>% count()
station_count <- seamap %>% count()
overall_se    <- round(sd(seamap$cpue_towspd, na.rm = T) / sqrt(station_count), 3)
